On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-21 paper.tex
Slightly rewritten text

The following lemma is similar to~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
\begin{lemma}
 Suppose $m \geq 1$.
 Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
 Assume, moreover, that $\xi \in B_k$, $\xi' \in B_{k'}$, $\eta \in B_l$, $\eta' \in B_{l'}$ are such that 
  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $k,k',l,l'\leq m$ satisfying $k+l=k'+l' = m+1$.
 Then the following relations holds in $G_m$:
 \begin{equation}
  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
 \end{equation}
 Moreover for every $\zeta \in B_{k''}$, $k''\leq m$ and $\gamma\in\{\alpha, \beta, \alpha + \beta\}$
  the following relation holds in $G_m$:
 \begin{equation}
 \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
 \end{equation}
\end{lemma}
\begin{proof}
 Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
 Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim in our situation.
 %TODO: Write down this argument, at least a part of it?
\end{proof}

@@

\begin{lemma} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
 $a\in A$, $\xi \in B_k$, $k \leq 0$ the following relation holds in $G_m$: 
\begin{equation}
\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)].
\end{equation}
\end{lemma}
\begin{proof}
By \cite[Lemma~3.1.2]{RS76} we can assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
\begin{align*}
   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
 = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
 = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$}
\end{align*} 
There are two cases.
\begin{enumerate}
 \item \label{case:cm-1} Case $m=1$, $k = 0$.
 \begin{align*}
   RHS  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$.}\\
        = [x_\alpha(t\xi), x_\beta(at^m)]                                 & \text{ by~\eqref{item:i}. }   
 \end{align*}  
 This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. Why is this true?

 \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $k < 0$.
 \begin{align*}
 RHS = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
 %TODO: There's a mistake at this moment --- k = 0, m = 1 and the needed relation is not in G_1 -- :(
 = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
 = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}.}
\end{align*}

@@

Now, let us show that relations $(b_{m+1})$ hold. 
Without loss of generality we may also assume $k \leq l=m+1$, thus $\eta = bt^{m+1}$ for some $b\in A$.

\begin{enumerate}
\item \label{case:1} First consider the case $k \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  As before, without loss of generality we may assume that $\alpha, \alpha'$ are contained in a root system $\Psi$ of type $\mathsf{A}_3$,
   whose simple roots are labeled as in~\eqref{eq:diagA3} and, moreover, $\alpha'=\alpha + \beta$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we get (recall that $\xi \in B_k$):
   \begin{multline} \nonumber
   [x_\alpha(\xi), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
  \end{multline}
  \item Case $\alpha \perp \alpha'$. As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [x_\alpha(\xi), x_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(bt^m), x_{-\beta}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\beta+\gamma}(bt^m)], {}^{x_{\beta+\gamma}(bt^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(bt^m)}\![x_{\alpha+\beta+\gamma}(bt^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}

\item \label{case:2} Now assume $1 \leq k \leq m+1$. 
At first we want to prove $(b_{m+1})$ only in the special case $\xi=t^k$.
We proceed by induction on $k$ starting with $k=1$.
Again, there are two cases.
\begin{enumerate}
 \item \label{case:2a} Case $\alpha\not\perp\alpha'$ is handled similarly to the Case~\eqref{case:1a} with the only
  difference that we have to refer to the inductive assumption rather than~\eqref{eq:bm} in the case $k=m+1$.
  \begin{multline} \nonumber
   [x_\alpha(t^k), x_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(t^k), [x_{\alpha+\beta+\gamma}(bt^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(t^k), x_{\alpha+\beta+\gamma}(bt^m)], {}^{x_{\alpha+\beta+\gamma}(bt^m)}\!x_{-\gamma}(t)] = 1.
  \end{multline}

 \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
\begin{align*}
{}^{x_\gamma(t^k)}x_\alpha(bt^{m+1}) = {}^{x_\gamma(t^k)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by $(c_{m+1})$}\\
 = [x_{-\beta}(b't^{m+1}), {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-k}), x_\gamma(t^k)], {}^{x_\gamma(t^k)}x_{\alpha+\beta}(1)]          & \text{ by $(c_{m+1})$}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-k)}), [x_\gamma(t^k), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-k \leq m$}\\
 = x_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_{m+1})$.} \end{align*}
 Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
 \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
\end{enumerate}
Thus we have demonstrated $(b_{m+1})$ in the special case $a=1$.
\item Now let us prove $(b_{m+1})$ for arbitrary $\xi = at^k$, $a\in A$ and $1\leq k\leq m+1$. Again, there are two subcases.
\begin{enumerate}
\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
 \begin{align*} [x_\alpha(at^k), x_{\alpha + \beta}(bt^{m+1})] = [x_\alpha(at^k), [x_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b)]] & \text{ by $(c_{m+1})$} \\
  = [[x_\alpha(at^k), x_{\alpha+\beta+\gamma}(t^{m+1})], {}^{x_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b)] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
\item Case $\alpha \perp \alpha'$.
 % mu        0  1 m+1
 % vu        1  0 k
 % mu'       0  1 m+1-k
 % mu - mu'  0  0 k
 % nu + mu'  1  1 m+1
 %           a  b t
The required identity follows from the following chain of equalities:
\begin{align*}
 x_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{x_{-\beta}(t^k)}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
 = {}^{x_{-\beta}(t^k)}\![x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(c_{m+1})$} \\
 = [x_{\alpha}(bt^{m+1}) x_{\alpha+\beta}(bt^{m+1-k}), x_\gamma(at^k)] & \text{ by $(b_k)$ or Case~\eqref{case:2} if $k=m+1$ }\\
 = {}^{x_{\alpha}(bt^{m+1})}\!x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by~\eqref{eq:H1ii} and $(c_{m+1})$} \\
 = x_{\alpha+\beta+\gamma}(abt^{m+1}) [x_{\alpha}(bt^{m+1}), x_\gamma(at^k)] & \text{ by Case~\eqref{case:3a}.}
\end{align*}
\end{enumerate}
\end{enumerate}

>>>>

The following lemma is similar to~\cite[Proposition 1.1]{Re75} and~\cite[Proposition~3.2.2]{RS76}.
\begin{lemma}
 Suppose $m \geq 1$.
 Let $\alpha, \beta, \alpha', \beta' \in \Phi$ be such that $\alpha + \beta = \alpha' + \beta'$.
 Assume, moreover, that $\xi \in B_d$, $\xi' \in B_{d'}$, $\eta \in B_e$, $\eta' \in B_{e'}$ are such that 
  $N_{\alpha, \beta} \xi \eta = N_{\alpha', \beta'}\xi' \eta'$ for some $d,d',e,e'\leq m$ satisfying $d+e=d'+e' = m+1$.
 Then the following relations holds in $G_m$:
 \begin{equation}
  \label{item:i} [x_\alpha(\xi), x_\beta(\eta)] = [x_{\alpha'}(\xi'), x_{\beta'}(\eta')].
 \end{equation}
 Moreover for every $\zeta \in B_{k''}$, $k''\leq m$ and $\gamma\in\{\alpha, \beta, \alpha + \beta\}$
  the following relation holds in $G_m$:
 \begin{equation}
 \label{item:ii} [[x_\gamma(\zeta), [x_\alpha(\xi), x_\beta(\eta)]] = 1.
 \end{equation}
\end{lemma}
\begin{proof}
 Notice that $k+l = m+1$, $k, l\leq m$ imply $k,l>0$, hence $B_i= t^i \cdot A$ for $i=k,k',l,'l'$.
 Thus, the argument of~\cite[Proposition 1.1]{Re75} can be repeated verbatim in our situation.
 %TODO: Write down this argument, at least a part of it?
\end{proof}

@@

\begin{lemma} \label{lem:bmp1} Suppose that $m\geq 1$. For every $\alpha, \alpha' \in \Phi$ such that $\alpha+\alpha' \in \Phi$ and
 $a\in A$, $\xi \in B_d$, $d \leq 0$ the following relation holds in $G_m$: 
\begin{equation}
\label{eq:verify-bmp1} [x_\alpha(\xi), S_{\alpha'}(at^{m+1})] = [x_\alpha(t\xi), x_{\alpha'}(at^m)] = S_{\alpha+\alpha'}(N_{\alpha,\alpha'}a\xi t^{m+1}).
\end{equation}
\end{lemma}
\begin{proof}
By \cite[Lemma~3.1.2]{RS76} we may assume without loss of generality that $\alpha'=\beta$ for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
\begin{align*}
   [x_\alpha(\xi), S_\beta(at^{m+1})] = [x_\alpha(\xi), [x_{\beta + \gamma}(t), x_{-\gamma}(a't^m)]]&  \text{ by~\eqref{item:i},\eqref{eq:defmpn} for $a' = N_{\beta+\gamma, -\gamma} a$} \\ 
 = [x_{\alpha+\beta+\gamma}(\epsilon t\xi), {}^{x_{\beta+\gamma}(t)}x_{-\gamma}(a't^m)]             &  \text{ by~\eqref{eq:H1iii}, for $\epsilon=N_{\alpha, \beta+\gamma}$} \\
 = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)]             &  \text{ by $(b_1)$}
\end{align*} 
Denote by $R$ the expression in the right hand side of the above formula.
\begin{enumerate}
 \item \label{case:cm-1} Case $m=1$, $d = 0$.
 \begin{align*}
   R  = [x_{\alpha +\beta + \gamma}(\epsilon t\xi), x_{-\gamma}(a't^m)] & \text{ by $(d_1)$}\\
        = [x_\alpha(t\xi), x_\beta(at^m)]                               & \text{ by~\eqref{item:i}. }   
 \end{align*}  
 This uses $N_{\alpha, \beta+\gamma} N_{\alpha+\beta+\gamma, -\gamma} N_{\beta+\gamma, -\gamma} = N_{\alpha, \beta}$. Why is this true?

 \item \label{case:cm-2} Case $m\geq 2$ or $m=1$, $d < 0$.
 \begin{align*}
 R = {}^{x_{\beta+\gamma}(t)}[x_{\alpha+\beta+\gamma}(\epsilon t^2\xi), x_{-\gamma}(a't^{m-1})]       &  \text{ by~\eqref{item:i} if $k=0$ or~\eqref{eq:cm} if $k <0$} \\
 = [[x_\alpha(t\xi), x_{\beta+\gamma}(t)], {}^{x_{\beta+\gamma}(t)} x_{-\gamma}(a't^{m-1})]         &  \text{ by~$(b_2)$, $(c_2)$ or by~\eqref{item:ii},\eqref{eq:defmpn} if $m=1$} \\
 = [x_\alpha(t\xi), x_\beta(at^m)]                                                                  &  \text{ by~\eqref{eq:H1iii}. \qedhere}
\end{align*}

@@

It will be convenient for us to extend the definition of $S_\alpha(\xi)$ by allowing $\xi$ to take values in $B_d$ for $d\leq m$.
In this case we simply set $S_\alpha(\xi) = x_\alpha(\xi)$.
\begin{lemma}
 For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
 the following relation holds in $G_m$:
  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
\end{lemma}
\begin{proof}
Write $\eta = bt^{m+1}$ for some $b\in A$.
\begin{enumerate}
\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
   \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
  \end{multline}
  %What this really proves: $b_{m}(\alpha, |\xi|, -\gamma, 1)$ and $b_m(\alpha, |\xi|, \alpha+\beta+\gamma, m)$ implies $b_{m+1}(\alpha, |\xi|, \alpha+\beta, m+1 )$.
  \item Case $\alpha \perp \alpha'$. 
  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [x_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [x_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}

\item \label{case:2} Now assume $1 \leq d \leq m+1$.
At first we want to prove~\eqref{eq:verify-bmp2} only in the special case $\xi=t^d$,
We proceed by induction on $d$, so we can assume that \eqref{eq:verify-bmp2} holds for $\xi = t^e$, $e<d$.
Again, there are two subcases.
\begin{enumerate}
 \item \label{case:2a} Case $\alpha\not\perp\alpha'$ is handled similarly to the Case~\eqref{case:1a} with the only
  difference that we must refer to the inductive assumption instead of~\eqref{eq:bm} in the case $d=m+1$:
  %TODO: No real induction going on here...
  \begin{multline} \nonumber
   [S_\alpha(t^d), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(t^d), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[S_\alpha(t^d), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1.
  \end{multline}

 \item Case $\alpha\perp\alpha'$. As before, we may assume $\alpha'=\gamma$.
\begin{align*}
{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[x_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] & \text{ by~\cref{lem:bmp1}}\\
 = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     & \text{ by Case~\eqref{case:2a} since $\gamma\not\perp-\beta$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           & \text{ by~\eqref{eq:H1iii} and~\eqref{eq:bm} since $m+1-d \leq m$}\\
 = S_{\alpha}(b'''t^{m+1})                                                                            & \text{ by $(c_m)$,\eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \end{align*}
 Usual identities for structure constants imply (cf.~\cite[p.~12]{Re75}):
 \[b'''=N_{-\beta-\gamma, \alpha+\beta+\gamma} \cdot N_{\gamma, \alpha+\beta} \cdot N_{-\beta-\gamma, \gamma} \cdot N_{-\beta, \alpha+\beta} \cdot b = b, \] 
\end{enumerate}
This finishes the proof of~\eqref{eq:verify-bmp2} in the special case $a=1$.
\item Now we deduce~\eqref{eq:verify-bmp2} for arbitrary $\xi = at^d$, $a\in A$ and $1\leq d\leq m+1$. Again, there are two subcases.
\begin{enumerate}
\item \label{case:3a} Case $\alpha \not\perp \alpha'$. % not possible to induct on k here :(
 \begin{align*} 
 [S_\alpha(at^d), S_{\alpha + \beta}(bt^{m+1})] = 
 [S_\alpha(at^d), [S_{\alpha+\beta+\gamma}(t^{m+1}), x_{-\gamma}(b')]] & \text{ by~\cref{lem:bmp1}} \\
  = [[x_\alpha(at^d), S_{\alpha+\beta+\gamma}(t^{m+1})], {}^{S_{\alpha+\beta+\gamma}(t^{m+1})}\!x_{-\gamma}(b')] & \text{ by $(b_k)$ or Case~\eqref{case:1} if $k=m+1$} \\
  = 1 & \text{ by Case~\eqref{case:2}.} \end{align*}
\item Case $\alpha \perp \alpha'$.
\begin{align*}
 S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) & \text{ by Case~\eqref{case:2}}\\
 = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
 = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] & \text{ by~\cref{lem:bmp1} and $(b_d)$ if $d\leq m$ or Case~\eqref{case:2} if $d=m+1$ }\\
 = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by~\eqref{eq:H1ii} and by \eqref{lem:bmp1},\eqref{eq:defmpn} or~\cref{lem:bmp1} if $d=m+1$} \\
 = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] & \text{ by Case~\eqref{case:3a},}
\end{align*}
from which the required identity follows. \qedhere
\end{enumerate}
\end{enumerate}
\end{proof}
